Search Strategies for Functional Logic Programming

### 2012-01-17 papers/atps2012/paper.tex

>>>>

In principle, the operator to encapsulate search can be
also used to implement an interactive top-level
to print all values of an expression as requested by the user.
For instance, the following operation prints all elements
of a given list as requested by the user:
\begin{curry}
printResults :: [_] -> IO ()
printResults [] = putStrLn "No more values"
printResults (x:xs) =
  do print x
     putStr "More values? "
     inp <- getLine
     if inp=="yes" then printResults xs
                   else done
\end{curry}
Hence, a Prolog-like top-level interactive environment
to show all values of an expression $exp$ in depth-first order
can be obtained by
\begin{curry}
getSearchTree $exp$ >>= printResults . allValuesDFS
\end{curry}
In addition, we can print the results in breadth-first order
by using \code{allValuesBFS} instead of \code{allValuesDFS}.
Based these ideas, KiCS2 provides an interactive top-level
where the user can select various search strategies
(depth-first, breadth-first, iterative deepening, parallel).
However, the top-level search in KiCS2 is not implemented
via the primitive encapsulation operator but in more direct
monadic style (see also \cite{BrasselHanusPeemoellerReck11})
in order to avoid the explicit construction
of the \code{SearchTree} structure.
